---
output:  html_document
number_sections: true
title: "FHAST Adult Summary"
header-includes:
    - \usepackage{setspace}\singlespacing
    - \usepackage{float}
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=0.2in
fontsize: 16pt
fig_caption: yes
indent: true
---
 <font size="4">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, knitr::opts_chunk$set(warning = FALSE, message = FALSE))
library(here)

```

```{r load_data, include=FALSE}

fish_migration_stats = ml$table$migration_summary_stats

fish_migration_map = here(ml$path$output_folder,  "migration_map.png")

fish_migration_hist = here(ml$path$output_folder,  "migration_energy_hist.png")

```

```{r pre_rrocess, include=FALSE}
fish_list = as.list(unique(ml$df$fish_combos$species))
n = 0
```

### Simulation name: `r ml$var$run_name`
***
## Tabular Outputs 
```{r print_fish_migration_stats, echo = FALSE}
fish_count <- length(unique(fish_migration_stats$species))

kable(fish_migration_stats,
      caption = paste0("The fish summary statistics for adult migration of the ", fish_count, " specie(s) of fish."),
      col.names = c("Species", "Energy Use (j)"))
```

\newpage
## Figures Outputs

```{r print_fish_migration_map, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(fish_migration_map,  error = FALSE)
```
**Fig. `r (n = n + 1)`** A set of maps showing the most used migration paths for the adult migrants of the fish species (`r unique(fish_migration_stats$species)`). <br><br><br><br>

```{r print_fish_migration_hist, echo = FALSE, out.width = "100%", fig.align="center"}
knitr::include_graphics(fish_migration_hist,  error = FALSE)
```
**Fig. `r (n = n + 1)`** A set of histograms showing the energy expenditure for the adult migrants of the fish species (`r unique(fish_migration_stats$species)`). <br><br><br><br>

\newpage
## Appendix
### Run inputs
The main input file:
```{r, echo=FALSE}
cat(readLines(file.path(here(ml$path$output_folder, "input_file.txt"))), sep = '\n')
```
---

The daily input file:
```{r, echo=FALSE, }
cat(readLines(file.path(here(ml$path$output_temp_folder,  "daily_input.txt"))), sep = '\n')
```
---

The interaction input file:
```{r, echo=FALSE, }
cat(readLines(file.path(here(ml$path$output_temp_folder,  "interactions_input.txt"))), sep = '\n')
```
---

The fish population file:
```{r, echo=FALSE, }
cat(readLines(file.path(here(ml$path$output_temp_folder,  "population_input.txt"))), sep = '\n')
```
---

The fish parameter file:
---
```{r, echo=FALSE, }
cat(readLines(file.path(here(ml$path$output_temp_folder,  "fish_input.txt"))), sep = '\n')
```
---

The habitat parameter file:
```{r, echo=FALSE, }
cat(readLines(file.path(here(ml$path$output_temp_folder,  "habitat_input.txt"))), sep = '\n')
```
---

The predator input file:
```{r, echo=FALSE, }
cat(readLines(file.path(here(ml$path$output_temp_folder,  "predator_input.txt"))), sep = '\n')
```
---
</font>
